---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
library(ggplot2)
library(tidymodels)
library(ISLR)

library(ISLR2)

library(discrim)
library(poissonreg)
library(corrr)
library(klaR)
tidymodels_prefer()
set.seed(2225)
library(corrplot)


```

### Question 1

Split the data, stratifying on the outcome variable, `survived.`  You should choose the proportions to split the data into. Verify that the training and testing data sets have the appropriate number of observations. Take a look at the training data and note any potential issues, such as missing data.

Why is it a good idea to use stratified sampling for this data?

stratified sampling is useful for this data because it uses specific characteristics, and it can provide more accurate representation of the population based on what is used to divide it into different subsets. 

```{r}
titanic <- read.csv("titanic.csv")

titanic$survived <- factor(titanic$survived, levels = c('Yes','No'))
titanic$pclass <- factor(titanic$pclass)

titanic_split <- initial_split(titanic, prop = 0.80,
                                strata = survived)

titanic_train <- training(titanic_split)
titanic_test <- testing(titanic_split)



```



### Question 2

Using the **training** data set, explore/describe the distribution of the outcome variable `survived`.
```{r}
ggplot(titanic_train,aes(x=survived)) + geom_bar()






```

### Question 3

Using the **training** data set, create a correlation matrix of all continuous variables. Create a visualization of the matrix, and describe any patterns you see. Are any predictors correlated with each other? Which ones, and in which direction?


Through the graph, it seems like it has a pattern of having grey colors on the missing value, which is on the middle of graph. Each same value is located on same location of x and y.
```{r}


cor_titanic_train <- titanic_train %>%
  select(is.numeric) %>%
  correlate()
rplot(cor_titanic_train)

cor_titanic_train %>%
  stretch() %>%
  ggplot(aes(x, y, fill = r)) +
  geom_tile() +
  geom_text(aes(label = as.character(fashion(r))))

```








### Question 4

Using the **training** data, create a recipe predicting the outcome variable `survived`. Include the following predictors: ticket class, sex, age, number of siblings or spouses aboard, number of parents or children aboard, and passenger fare.

Recall that there were missing values for `age`. To deal with this, add an imputation step using `step_impute_linear()`. Next, use `step_dummy()` to **dummy** encode categorical predictors. Finally, include interactions between:

-   Sex and passenger fare, and
-   Age and passenger fare.

You'll need to investigate the `tidymodels` documentation to find the appropriate step functions to use.

```{r}

titanic_recipe <- recipe(survived ~ pclass + sex + age + sib_sp + parch + fare , data = titanic_train) %>%
  step_impute_linear(age) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_interact(terms = ~ starts_with("sex"):fare + age:fare)






```









### Question 5

Specify a **logistic regression** model for classification using the `"glm"` engine. Then create a workflow. Add your model and the appropriate recipe. Finally, use `fit()` to apply your workflow to the **training** data.

***Hint: Make sure to store the results of `fit()`. You'll need them later on.***


```{r}

log_reg <- logistic_reg() %>%
  set_engine("glm")%>%
  set_mode("classification")
log_wkflow <- workflow() %>%
  add_model(log_reg) %>%
  add_recipe(titanic_recipe)
log_fit <- fit(log_wkflow, titanic_train)
  






```










### Question 6

**Repeat Question 5**, but this time specify a linear discriminant analysis model for classification using the `"MASS"` engine.



```{r}
lda_mod <- discrim_linear() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

lda_wkflow <- workflow() %>% 
  add_model(lda_mod) %>% 
  add_recipe(titanic_recipe)

lda_fit <- fit(lda_wkflow, titanic_train)







```







### Question 7

**Repeat Question 5**, but this time specify a quadratic discriminant analysis model for classification using the `"MASS"` engine.


```{r}

qda_mod <- discrim_quad() %>% 
  set_mode("classification") %>% 
  set_engine("MASS")

qda_wkflow <- workflow() %>% 
  add_model(qda_mod) %>% 
  add_recipe(titanic_recipe)

qda_fit <- fit(qda_wkflow, titanic_train)



```







### Question 8

**Repeat Question 5**, but this time specify a naive Bayes model for classification using the `"klaR"` engine. Set the `usekernel` argument to `FALSE`.





```{r}

nb_mod <- naive_Bayes() %>% 
  set_mode("classification") %>% 
  set_engine("klaR") %>% 
  set_args(usekernel = FALSE) 

nb_wkflow <- workflow() %>% 
  add_model(nb_mod) %>% 
  add_recipe(titanic_recipe)

nb_fit <- fit(nb_wkflow, titanic_train)


```





### Question 9

Now you've fit four different models to your training data.

Use `predict()` and `bind_cols()` to generate predictions using each of these 4 models and your **training** data. Then use the *accuracy* metric to assess the performance of each of the four models.

Which model achieved the highest accuracy on the training data?

Logistic regression achieved the highest accuracy on the training data.
```{r}
log_reg_acc <- augment(log_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)

lda_acc <- augment(lda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)

qda_acc <- augment(qda_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)

nb_acc <- augment(nb_fit, new_data = titanic_train) %>%
  accuracy(truth = survived, estimate = .pred_class)



accuracies <- c(log_reg_acc$.estimate, lda_acc$.estimate, 
                nb_acc$.estimate, qda_acc$.estimate)
models <- c("Logistic Regression", "LDA", "Naive Bayes", "QDA")
results <- tibble(accuracies = accuracies, models = models)
results %>% 
  arrange(-accuracies)


```







### Question 10

Fit the model with the highest training accuracy to the **testing** data. Report the accuracy of the model on the **testing** data.

Again using the **testing** data, create a confusion matrix and visualize it. Plot an ROC curve and calculate the area under it (AUC).

How did the model perform? Compare its training and testing accuracies. If the values differ, why do you think this is so?


From ROC graph, the graph model looks good, which is only 0.07 value differnece compare to training data. I think training and testing accuracy is different because the model is optimized for the latter. So that is why test accuracy is not higher than train accuracy. 




```{r}
predict(log_fit, new_data = titanic_test, type = "prob")

augment(log_fit, new_data = titanic_test) %>%
  conf_mat(truth = survived, estimate = .pred_class) %>%
  autoplot(type = "heatmap")

augment(log_fit, new_data = titanic_test) %>%
  roc_auc(truth = survived, estimate = .pred_Yes)


multi_metric <- metric_set(accuracy, sensitivity, specificity)

augment(nb_fit, new_data = titanic_test) %>%
  multi_metric(truth = survived, estimate = .pred_class)


augment(log_fit, new_data = titanic_test) %>%
  roc_curve(survived, .pred_Yes) %>%
  autoplot()








```



